DRAFT Example Kitsap County Pedestrian Facilities Metrics/Evaluation Report

### 2022-10-03 child_single_geo.Rmd
correct placeholders

```{r} 
library(broom)
this_geo <- st_as_sf(loop_df) %>% filter(tomatch == current_geo) #"{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))

>>>>

```{r} 
library(broom)
this_geo <- st_as_sf(loop_df) %>% filter(tomatch == "{{current_geo}}") 
this_roads <- st_intersection(road_df, st_buffer(this_geo,0))
this_sw_sh <- st_intersection(nc_sw_sh, st_buffer(this_geo,0))
